### 2024-11-26 paper/eval.tex
Minor change

% 7 + 3 + ??? + 44
% TODO: Fill number
% TODO: Add cite
\section{RQ2: Generality}
We evaluate AL's generality by applying SpecTec to eight proposals prepared for
inclusion in the next version of Wasm: typed function references
~\cite{proposal-fr}, garbage collection~\cite{propsal-gc}, tail calls
~\cite{proposal-tc}, multiple memories~\cite{proposal-mm}, extended constant
expressions~\cite{proposal-ec}, memory64~\cite{proposal-m64}, relaxed SIMD
~\cite{proposal-rs}, exception handling~\cite{proposal-eh}.
This proposals add or modify ??? Wasm instructions.
In particular, the garbage collection proposal adds substantial complications
to the Wasm type system, and the exception handling proposal introduces a new
context, \textit{handler}.
Notably, specifying all eight proposals in AL requires only trivial
adjustments, such as adding a handler case to the context.

>>>>

% 7 + 3 + ??? + 44
% TODO: Fill number
% TODO: Add cite
\section{RQ2: Generality}
We evaluate AL's generality by applying SpecTec to eight proposals prepared for
inclusion in the next version of Wasm: typed function references
~\cite{proposal-fr}, garbage collection~\cite{propsal-gc}, tail calls
~\cite{proposal-tc}, multiple memories~\cite{proposal-mm}, extended constant
expressions~\cite{proposal-ec}, memory64~\cite{proposal-m64}, relaxed SIMD
~\cite{proposal-rs}, exception handling~\cite{proposal-eh}.
This proposals add or modify ??? Wasm instructions.
In particular, the garbage collection proposal adds substantial complications
to the Wasm type system, and the exception handling proposal introduces a new
context, \textit{handler}.
Notably, specifying all eight proposals in AL requires only trivial
adjustments: adding a handler case to the context and generalizing AL
instruction for describing Wasm runtime errors.
